Windowed least-squares model reduction for dynamical systems

### 2019-10-23 numerical_experiments.tex
updated fig 6

\begin{figure}
\begin{center}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_fom.pdf}
\caption{Full-order model}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_grom.pdf}
\caption{G-ROM}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_lspg.pdf}
\caption{LSPG}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_w1.pdf}
\caption{\methodAcronym: $\DeltaSlabArg{}= 0.002$}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_w50.pdf}
\caption{\methodAcronym: $\DeltaSlabArg{} = 0.1$}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_w500.pdf}
\caption{\methodAcronym: $\DeltaSlabArg{} = 1.0$}
\end{subfigure}
\caption{$x-t$ diagrams for the density fields as predicted by the FOM, G-ROM,
	LSPG-ROM, and \methodAcronymROMs. \KTC{Xlabel should be `spatial variable
	$\mathcal x$. Ylabel should be `time $t$'. I wouldn't call this an $x-t$
	diagram; I'd call is a density-solution plot}}
\label{fig:sod_xt}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_fom.pdf}
\caption{Full-order model}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_grom.pdf}
\caption{G-ROM}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_lspg.pdf}
\caption{LSPG}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_w1.pdf}
\caption{\methodAcronym: $\DeltaSlabArg{}= 0.002$}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_w50.pdf}
\caption{\methodAcronym: $\DeltaSlabArg{} = 0.1$}
\end{subfigure}
\begin{subfigure}[t]{0.48\textwidth}
\includegraphics[width=1.\linewidth]{figs/sod/xt_w500.pdf}
\caption{\methodAcronym: $\DeltaSlabArg{} = 1.0$}
\end{subfigure}
\caption{$\mathsf{x}-t$ diagrams for the density fields as predicted by the FOM, G-ROM,
	LSPG-ROM, and \methodAcronymROMs. \EP{I am going to stick with $x-t$ diagram, I feel like this is the standard terminology}}
\label{fig:sod_xt}
\end{center}
\end{figure}
